The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-12 document/ms.tex
more prediction work, intro FP sentences

Tim to write some words here.

>>>>

Various configurations of grazing or blended eclipsing binaries can mimic the
signal of a transiting planet \citep{}. The occurrence rate calculation
presented in the preceding section assumes that none of the planet
candidates identified in this work are caused by such astrophysical false
positives.  In this Section we explore the validity of this assumption.
